---
title: "p8105_hw1_cl3938"
output: github_document
---

```{r}
library(tidyverse)
library(palmerpenguins)
```

## Problem 1

Creating a data frame of:
  - a random sample of size 10 from a standard Normal distribution
  - a logical vector indicating whether elements of the sample are greater than 0
  - a character vector of length 10
  - a factor vector of length 10, with 3 different factor “levels”
  
```{r df_init}
p1_df = tibble(
  samp_rand_norm = rnorm(10),
  bin_if_positive = samp_rand_norm > 0,
  vec_char = c("I", "am", "doing", "my", "hw", "very", "last", "minute", "I'm", "sorry"),
  vec_factor = factor(c("blue", "blue", "brown", "green", "green", "brown", "brown", "brown", "brown", "blue"))
)

```
Taking the mean of the dataframe gets me:

```{r mean_vector_var}
mean(pull(p1_df, samp_rand_norm))
mean(pull(p1_df, bin_if_positive))
mean(pull(p1_df, vec_char))
mean(pull(p1_df, vec_factor))
```

I can only get the mean of numbers and logical vectors but not character or factor vectors. 

```{r eval = FALSE}
as.numeric(pull(p1_df, samp_rand_norm))
as.numeric(pull(p1_df, bin_if_positive))
as.numeric(pull(p1_df, vec_char))
as.numeric(pull(p1_df, vec_factor))
```

The as.numeric function works numbers, logicals, and factors but not characters. The factor variable 'levels' work with as.numeric, like a categorical variable. 

```{r as_numeric_rand }
as.numeric(pull(p1_df, bin_if_positive))  * pull(p1_df, samp_rand_norm)
as.factor(pull(p1_df, bin_if_positive))  * pull(p1_df, samp_rand_norm)
as.numeric(as.factor(pull(p1_df, bin_if_positive))) * pull(p1_df, samp_rand_norm)
```

The result from logical conversion factor, multiplied by the random sample is not meaningful because is a factor does not have numerical value. It's the equivalent of multiplying a categorical variable by a continuous one.

## Problem 2

Some info about penguins

```{r penguin_data}
data("penguins", package = "palmerpenguins")
summary(penguins)
view(penguins)
```
This data set has 344 observations, with `r nrow(penguins)` rows and `r ncol(penguins)` columns. 

The variables in the dataset: species, island, bill length, bill depth, flipper length, body mass, sex, and year. 

The species of interest are Adelie, Chinstrap, and Gentoo penguins on the islands of Biscoe, Dream, and Torgersen.

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`. 

Next, an analysis of flipper vs bill length in these penguins
```{r peng_scatter}

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("penguins_bill_flipper_comparison.pdf")
```
