---
title: "p8105_hw1_cl3938"
output: github_document
---

```{r}
library(tidyverse)
library(palmerpenguins)
```

## Problem 1

Creating a data frame of:
  - a random sample of size 10 from a standard Normal distribution
  - a logical vector indicating whether elements of the sample are greater than 0
  - a character vector of length 10
  - a factor vector of length 10, with 3 different factor “levels”
  
```{r df_init}
p1_df = tibble(
  samp_rand_norm = rnorm(10),
  bin_if_positive = samp_rand_norm > 0,
  vec_char = c("I", "am", "doing", "my", "hw", "very", "last", "minute", "I'm", "sorry"),
  vec_factor = factor(c("blue", "blue", "brown", "green", "green", "brown", "brown", "brown", "brown", "blue"))
)

```
Taking the mean of the dataframe gets me:

```{r mean_vector_var}
mean(pull(p1_df, samp_rand_norm))
mean(pull(p1_df, bin_if_positive))
mean(pull(p1_df, vec_char))
mean(pull(p1_df, vec_factor))
```

I can only get the mean of numbers and logical vectors but not character or factor because they are not numerical values. 

```{r eval = FALSE}
as.numeric(pull(p1_df, samp_rand_norm))
as.numeric(pull(p1_df, bin_if_positive))
as.numeric(pull(p1_df, vec_char))
as.numeric(pull(p1_df, vec_factor))
```

The as.numeric function works numbers, logicals, and factors but not characters. The factor variable 'levels' work with as.numeric, like a categorical variable. 

```{r as_numeric_rand }
as.numeric(pull(p1_df, bin_if_positive))  * pull(p1_df, samp_rand_norm)
as.factor(pull(p1_df, bin_if_positive))  * pull(p1_df, samp_rand_norm)
as.numeric(as.factor(pull(p1_df, bin_if_positive))) * pull(p1_df, samp_rand_norm)
```

The result from logical conversion factor, multiplied by the random sample is not meaningful because is a factor does not have numerical value and cannot be multiplied. It's the equivalent of multiplying a categorical variable by a continuous one.

## Problem 2


```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
